---
title: "Home Work 04"
author: "Greg Sheng"
date: "2023-11-12"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
setwd("C:/Users/User/Desktop/CASA0005 GIS/R_study/ass4")
knitr::opts_chunk$set(echo = TRUE)
```

## Load lobraries
```{r}
library(readr)
library(dplyr)
library(sf)  # for read shp file
library(tidyverse)


```


## Read the global gender inequality data

```{r}
gender_data <- read.csv("C:/Users/User/Desktop/CASA0005 GIS/R_study/ass4/Data/HDR21-22_Composite_indices_complete_time_series.csv")

```


## Read world countries shp file

```{r}
World_Countries <-st_read ("C:/Users/User/Desktop/CASA0005 GIS/R_study/ass4/Data/World_Countries_Generalized/World_Countries_Generalized.shp")

```

## manipulate data

```{r}
cleaned_gender_data <- gender_data %>%
  select(country, iso3, gii_2019, gii_2010) %>%
  mutate(difference = gii_2019 - gii_2010) %>%
  drop_na() %>%
  left_join(.,World_Countries, by=c("country" = "COUNTRY"))

head(cleaned_gender_data)

```

### Code Learning Note

## Load lobraries
library(readr)
library(dplyr)
library(sf)  # for read shp file
library(tidyverse)



# Read csv
name read data <- read.csv("C:/ file_location/file_name.csv")

# Read read shp
name data  <-st_read ("C:/ file_location/file_name.shp")


# clean data :
name clean data  <- gender_data %>%

# select data
select(select data columns ie ax, bx, cx) %>% 
# mutate data
mutate(difference = gii_2019 - gii_2010) %>%
# drop data
drop_na() %>%
# join data
left_join(.,World_Countries, by=c("country" = "COUNTRY"))
# display data
head(data file name)




